Forecasting the 2024 U.S. Presidential Election: Kamala Harris' Projected Victory

### 2024-11-04 paper/paper.qmd
committing formatting changes to paper.qmd

#### State
The state (**'state'**) variable indicates the U.S. state where the poll was conducted or targeted. 
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-state-distribution
#| fig-cap: "Distribution of Observations for Each State in Polling Data. Illustrates the number of polling observations across key battleground statesn. Pennsylvania has the highest count of observations, suggesting a more robust polling presence, while Nevada shows fewer observations."

# Visualize the distribution of the state variable
ggplot(clean_poll_data, aes(x = state)) +
  geom_bar(fill = "steelblue") +  # Bar plot with specified fill color
  labs(
    x = "State",
    y = "Count of Observations"
  ) +
  theme_minimal() +  # Use a minimal theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for better readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  )
```
In the context of the U.S. presidential election, the outcome is frequently determined by several key battlegroud states. In the current 2024 election cycle, there are seven battleground states that are pivotal in the contest between Kamala Harris, representing the Democratic Party, and Donald Trump, representing the Republican Party. To enhance our model and refine our predictions, we focused exclusively on these seven battleground states. The polling results from each of these states play a crucial role in predicting electoral outcomes, as the percentage of support is evaluated on a state-by-state basis. The distribution of the state variable is visualized in @fig-state-distribution and indicates that some states, such as Pennsylvania, North Carolina and Wisconsin have more polling observations compared to others, like Nevada. This variability reflects differences in polling frequency and interest among these battleground states. States with more polling observations provide a larger sample size, potentially leading to more stable and reliable predictions for those states in the model.

>>>>

#### State
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-state-distribution
#| fig-cap: "Distribution of Observations for Each State in Polling Data. Illustrates the number of polling observations across key battleground statesn. Pennsylvania has the highest count of observations, suggesting a more robust polling presence, while Nevada shows fewer observations."

# Visualize the distribution of the state variable
ggplot(clean_poll_data, aes(x = state)) +
  geom_bar(fill = "steelblue") +  # Bar plot with specified fill color
  labs(
    x = "State",
    y = "Count of Observations"
  ) +
  theme_minimal() +  # Use a minimal theme
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels for better readability
    plot.title = element_text(hjust = 0.5)  # Center the plot title
  )
```
The state (**'state'**) variable indicates the U.S. state where the poll was conducted or targeted. In the context of the U.S. presidential election, the outcome is frequently determined by several key battlegroud states. In the current 2024 election cycle, there are seven battleground states that are pivotal in the contest between Kamala Harris, representing the Democratic Party, and Donald Trump, representing the Republican Party. To enhance our model and refine our predictions, we focused exclusively on these seven battleground states. The polling results from each of these states play a crucial role in predicting electoral outcomes, as the percentage of support is evaluated on a state-by-state basis. The distribution of the state variable is visualized in @fig-state-distribution and indicates that some states, such as Pennsylvania, North Carolina and Wisconsin have more polling observations compared to others, like Nevada. This variability reflects differences in polling frequency and interest among these battleground states. States with more polling observations provide a larger sample size, potentially leading to more stable and reliable predictions for those states in the model.
